New orbits for irregular satellites based on thousands of new observations and predictions of stellar occultations up to 2020

### 2016-05-25 Irregular-occ/Irregular-occ.tex
.

\title[New orbits and predictions of stellar occultations by irregular satellites up to 2020]{New orbits for irregular satellites based on thousands of new observations and predictions of stellar occultations up to 2020}
\author[A. R. Gomes-J\'unior, M. Assafin, L. Beauvalet et al.]{A. R. Gomes-J\'unior$^{1}$\thanks{E-mail: altair08@astro.ufrj.br},
M. Assafin$^{1,\dag}$,
L. Beauvalet$^{2,3}$,
J. Desmars$^{4}$,
R. Vieira-Martins$^{1,2,5,\dag}$,\newauthor
J. I. B. Camargo$^{2,5}$,
B. E. Morgado$^{1,2}$
F. Braga-Ribas$^{2,6}$
\\
$^{1}$Observat\'orio do Valongo/UFRJ, Ladeira Pedro Ant\^onio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
$^{2}$Observat\'orio Nacional/MCTI, R. General Jos\'e Cristino 77, CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
$^{3}$Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau 75014 Paris, France\\
$^{4}$Institut de m\'ecanique c\'eleste et de calcul des \'eph\'em\'erides - Observatoire de Paris, UMR 8028 du CNRS, 77 Av. Denfert-Rochereau,\\ 75014 Paris, France\\
$^{5}$Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil\\
$^{6}$Federal University of Technology - Paran\'a (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil
}
\begin{document}
\newcommand{\noccs}{5442 } % total number of occultations
\defcitealias{GomesJunior2015}{GJ15}

@@

In Table \ref{Tab:STE-error} it is presented the mean offsets of the \citetalias{GomesJunior2015} positions relative to the same 3 ephemeris as above. We can see that the mean offsets are highly reduced with the STE ephemeris.

\begin{table}
\caption{\label{Tab:STE-error} Mean offsets of the \protect\citetalias{GomesJunior2015} positions relative to the STE, \protect\cite{Jacobson2012} and \protect\cite{Emelyanov2008} ephemeris .}
\begin{centering}
\begin{tabular}{lcccccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
 & \multicolumn{2}{c}{STE} & \multicolumn{2}{c}{JPL} & \multicolumn{2}{c}{Eme2008}\tabularnewline
Satellite  & RA & DEC & RA & DEC & RA & DEC \tabularnewline
\hline
Ananke & $-10$ & $3$ & $60$ & $-108$ & $101$ & $-107$ \tabularnewline
Carme & $14$ & $-1$ & $-3$ & $-80$ & $-6$ & $-45$ \tabularnewline
Elara & $3$ & $-12$ & $20$ & $-50$ & $23$ & $-83$ \tabularnewline
Himalia & $-15$ & $-7$  & $-19$  & $-11$ & $-18$  & $-13$ \tabularnewline
Leda & $-9$ & $-8$ & $60$ & $-13$ & $166$ & $92$ \tabularnewline
Lysithea & $15$ & $-21$ & $40$ & $-43$ & $117$ & $-76$ \tabularnewline
Pasiphae & $4$ & $-16$ & $-17$ & $-82$ & $-10$ & $-54$ \tabularnewline
Sinope & $9$ & $-4$ & $10$ & $-35$ & $11$ & $-52$ \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table}

@@

We computed the precision of the PH15 ephemeris considering three sets of observations: all the positions available; only the positions of \citetalias{GomesJunior2015}; and all the positions without \citetalias{GomesJunior2015}. In Fig. \ref{Fig:err-Phoebe} is shown the comparison between them for the time spam 2016-2021. It is possible to see that even considering only the positions of \citetalias{GomesJunior2015}, the estimated error of the ephemeris is smaller than 12 mas. The computed precision does not take into account the precision in the position of Saturn.

\begin{figure}
\begin{centering}
\includegraphics[width=8.8cm]{figures/PH15_err_angsep.eps}  
\caption{Comparison of the precision of the PH15 ephemeris where three different sets of positions were used to compute the ephemeris: all observations; only positions of \citetalias{GomesJunior2015}; and all the positions without \citetalias{GomesJunior2015}.}
\label{Fig:err-Phoebe}
\end{centering}
\end{figure}

@@

As it was shown for Phoebe, when we use only the positions of \citetalias{GomesJunior2015}, the ephemeris presents a precision in the order of those where all the positions were used. Moreover, the case of Phoebe is particular because we have many observations in a large time spam (1898 to 2014) including observations from Cassini. For the Jovian satellites with less observations, the precision we have by using only \citetalias{GomesJunior2015} observations would be quite equivalent or even better than the precision of other ephemeris for the short time explored in this work.

>>>>

\title[New orbits and predictions of stellar occultations by irregular satellites up to 2020]{New orbits for irregular satellites based on thousands of new observations and predictions of stellar occultations up to 2020}
\author[A. R. Gomes-J\'unior, M. Assafin, L. Beauvalet et al.]{A. R. Gomes-J\'unior$^{1}$\thanks{E-mail: altair08@astro.ufrj.br},
M. Assafin$^{1,\dag}$,
L. Beauvalet$^{2,3}$,
J. Desmars$^{4}$,\newauthor
R. Vieira-Martins$^{1,2,5,\dag}$,
J. I. B. Camargo$^{2,5}$,
B. E. Morgado$^{1,2}$
F. Braga-Ribas$^{2,6}$
\\
$^{1}$Observat\'orio do Valongo/UFRJ, Ladeira Pedro Ant\^onio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
$^{2}$Observat\'orio Nacional/MCTI, R. General Jos\'e Cristino 77, CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
$^{3}$Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau 75014 Paris, France\\
$^{4}$Institut de m\'ecanique c\'eleste et de calcul des \'eph\'em\'erides - Observatoire de Paris, UMR 8028 du CNRS, 77 Av. Denfert-Rochereau,\\ 75014 Paris, France\\
$^{5}$Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil\\
$^{6}$Federal University of Technology - Paran\'a (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil
}
\begin{document}
\newcommand{\noccs}{5442 } % total number of occultations
\defcitealias{GomesJunior2015}{GJ15}

@@

In Table \ref{Tab:STE-error} it is presented the mean offsets and the respective standard deviation of the \citetalias{GomesJunior2015} positions relative to the same 3 ephemeris as above. We can see that the mean offsets are greatly reduced with the STE ephemeris.

\begin{table*}
\caption{\label{Tab:STE-error} Mean offsets and standard deviation of the \protect\citetalias{GomesJunior2015} positions relative to the STE, \protect\cite{Jacobson2012} and \protect\cite{Emelyanov2008} ephemeris .}
\begin{centering}
\begin{tabular}{l|cc|cc|cc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
 & \multicolumn{2}{|c|}{STE} & \multicolumn{2}{|c|}{JPL} & \multicolumn{2}{|c}{Eme2008}\tabularnewline
Satellite  & RA & DEC & RA & DEC & RA & DEC \tabularnewline
\hline
Ananke & $-10\pm90$ & $3\pm73$ & $60\pm127$ & $-108\pm99$ & $101\pm180$ & $-107\pm120$ \tabularnewline
Carme & $14\pm73$ & $-1\pm51$ & $-3\pm114$ & $-80\pm102$ & $-6\pm108$ & $-45\pm80$ \tabularnewline
Elara & $3\pm92$ & $-12\pm57$ & $20\pm92$ & $-50\pm69$ & $23\pm94$ & $-83\pm81$ \tabularnewline
Himalia & $-15\pm66$ & $-7\pm54$  & $-19\pm80$  & $-11\pm52$ & $-18\pm72$  & $-13\pm53$ \tabularnewline
Leda & $-9\pm67$ & $-8\pm77$ & $60\pm117$ & $-13\pm95$ & $166\pm162$ & $92\pm95$ \tabularnewline
Lysithea & $15\pm79$ & $-21\pm68$ & $40\pm92$ & $-43\pm77$ & $117\pm193$ & $-76\pm185$ \tabularnewline
Pasiphae & $4\pm89$ & $-16\pm57$ & $-17\pm130$ & $-82\pm85$ & $-10\pm102$ & $-54\pm74$ \tabularnewline
Sinope & $9\pm79$ & $-4\pm47$ & $10\pm228$ & $-35\pm76$ & $11\pm227$ & $-52\pm63$ \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table*}

@@

We computed the precision of the PH15 ephemeris considering three sets of observations: all the positions available; only the positions of \citetalias{GomesJunior2015}; and all the positions without \citetalias{GomesJunior2015}. In Fig. \ref{Fig:err-Phoebe} we show the comparison between them for the time spam 2016-2021 in angular separation of Saturn. It is possible to see that even considering only the positions of \citetalias{GomesJunior2015}, the estimated error of the ephemeris is smaller than 12 mas. The computed precision does not take into account the precision in the position of Saturn.

\begin{figure}
\begin{centering}
\includegraphics[width=8.8cm]{figures/PH15_err_angsep.eps}  
\caption{Comparison of the precision in angular separation of Saturn for the PH15 ephemeris where three different sets of positions were used to compute the ephemeris: all observations; only positions of \citetalias{GomesJunior2015}; and all the positions without \citetalias{GomesJunior2015}.}
\label{Fig:err-Phoebe}
\end{centering}
\end{figure}

@@

As it was shown for Phoebe, when we use only the positions of \citetalias{GomesJunior2015}, the ephemeris presents a precision in the order of those where all the positions were used. Moreover, the case of Phoebe is particular because we have many observations in a large time spam (1898 to 2014) including observations from Cassini. For the Jovian satellites with less observations, the precision we have by using only \citetalias{GomesJunior2015} observations would be quite equivalent or even better than the precision of other ephemeris for the short time span explored in this work.
